Self Regulation Ontology Retest Analyses

### 2018-05-14 code/SRO_Retest_Analyses.Rmd
plots for frisem

@@

```{r}
summary(duplicate_items$t1_t1_polycor)
summary(duplicate_items$t2_t2_polycor)
summary(duplicate_items$t1_t2_polycor)
summary(duplicate_items$t2_t1_polycor)
```

>>>>

for(i in 1:nrow(duplicate_items)){
  duplicate_items$t1_t1_cor[i] = abs(cor(scale(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])]),
                                  scale(duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])])))

  duplicate_items$t2_t2_cor[i] = abs(cor(scale(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])]),
                                  scale(duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])])))

  duplicate_items$t1_t2_cor[i] = abs(cor(scale(duplicate_items_data_t1[,c(duplicate_items$item1_ID[i])]),
                                  scale(duplicate_items_data_t2[,c(duplicate_items$item2_ID[i])])))

  duplicate_items$t2_t1_cor[i] = abs(cor(scale(duplicate_items_data_t2[,c(duplicate_items$item1_ID[i])]),
                                  scale(duplicate_items_data_t1[,c(duplicate_items$item2_ID[i])])))

@@

```{r}
summary(duplicate_items$t1_t1_cor)
summary(duplicate_items$t2_t2_cor)
summary(duplicate_items$t1_t2_cor)
summary(duplicate_items$t2_t1_cor)

summary(duplicate_items$t1_t1_polycor)
summary(duplicate_items$t2_t2_polycor)
summary(duplicate_items$t1_t2_polycor)
summary(duplicate_items$t2_t1_polycor)
```

Time 1: item 1 - item 2
Time 1 item 1 - time 2 item 2
Time 2 item 1 - time 1 item 2
Time 2: item 1 - item 2

```{r}
tmp = duplicate_items_data_t1 %>%
  gather(key, value, -worker)

tmp2 = duplicate_items_data_t2 %>%
  gather(key, value, -worker)

tmp = duplicate_items %>%
  select(item1_ID, item2_ID) %>%
  left_join(tmp, by = c("item1_ID" = "key")) %>%
  left_join(tmp, by = c("item2_ID" = "key", "worker" = "worker")) %>%
  rename(item1_time1 = value.x, item2_time1 = value.y) %>%
  left_join(tmp2, by = c("item1_ID" = "key", "worker" = "worker")) %>%
  left_join(tmp2, by = c("item2_ID" = "key", "worker" = "worker")) %>%
  rename(item1_time2 = value.x, item2_time2 = value.y) %>%
  group_by(item1_ID) %>%
  mutate(item1_time1 = scale(item1_time1),
         item1_time2 = scale(item1_time2),
         item2_time1 = scale(item2_time1),
         item2_time2 = scale(item2_time2)) %>%
  ungroup()

p1 = tmp %>%
  ggplot(aes(item1_time1, item2_time1, col=item1_ID))+
  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
  theme(legend.position = "none")+
  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
  xlab("Item 1 T1")+
  ylab("Item 2 T1")

p2 = tmp %>%
  ggplot(aes(item1_time1, item2_time2, col=item1_ID))+
  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
  theme(legend.position = "none")+
  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
  xlab("Item 1 T1")+
  ylab("Item 2 T2")

p3 = tmp %>%
  ggplot(aes(item1_time2, item2_time1, col=item1_ID))+
  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
  theme(legend.position = "none")+
  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
  xlab("Item 1 T2")+
  ylab("Item 2 T1")

p4 = tmp %>%
  ggplot(aes(item1_time2, item2_time2, col=item1_ID))+
  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
  theme(legend.position = "none")+
  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
  xlab("Item 1 T2")+
  ylab("Item 2 T2")

ggplotly(p1)

grid.arrange(p1, p2, p3, p4, ncol=2)

rm(tmp, tmp2)
```
